---
title: "p8105_hw5_zz2603"
author: "Ziyi Zhao"
date: "11/5/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

```


# Problem 1
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()

output <- vector("list",length = 5)

missiris <- function(x) {
    if (is.numeric(x)) {
      x[is.na(x)] = mean(x,na.rm = TRUE)
      } else if (is.character(x)) {
      x[is.na(x)] <- "virginica"
      }
  x
}

num_col = dim(iris_with_missing)[2]
for (i in 1:num_col) {
  output[[i]] = missiris(iris_with_missing[[i]])
}

output = map(iris_with_missing,missiris)

```

# Problem 2
```{r}
name_study <- list.files(path = "./hw5_data/data")

study_df <- tibble(name_study) %>% t() %>% as_tibble()

dtlst = vector("list",length = 20)
longdata <- function(x) {
  a = read_csv(paste0("./hw5_data/data/",x[[i]])) %>%
  t() %>% as_tibble()
  a
}

for (i in 1:20) {
  dtlst[[i]] = longdata(study_df)
}

dflst = vector("list",length = 20)
dflst[[1]] <- dtlst[[1]]
for (i in 2:20) {
  dflst[[i]] <- bind_cols(dflst[[i-1]],dtlst[i])  
}

finaldf <- dflst[[20]]
colnames(finaldf) <- substr(study_df[1,],1,6)
finaldf <- bind_cols(finaldf,tibble(Week = c(1:8)))

tidydf <- finaldf %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    con_01:exp_10,
    names_to = "Arm_ID",
    values_to = "Weekly_data"
  )

tidydf %>% 
  mutate(arm = substr(Arm_ID,1,3)) %>% 
  ggplot(aes(x=week,y=Weekly_data))+
  geom_line(aes(group=Arm_ID,color=arm))+
  scale_color_viridis(name="Arm",discrete = TRUE)+
  theme_classic()+
  labs(
    x="Time (Weeks)",
    y="Weekly Data",
    title = "Longitudinal Study"
  )+
  theme(
    plot.title = element_text(face = "bold")
  )

```

From the plot, we can find there is a general increasing trend in experiment group as the time increase. The data of two groups between week 2 are largely overlapped, but then the values of experiment group began to increase slightly as time p increase. The general trend among control group tends to be flat. Until week 6, most subjects in experiment group have greater values than values in control groups.

# Problem 3
```{r}


```









